The Puzzle of the Distinct Solitude Experiences in Our Daily Life

### 2022-04-27 outputs/paper/paper.Rmd
final version draft

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width=8,fig.height=4)
library(readr)
library(here)
library(tidyverse)
library(car)
library(dplyr)
library(patchwork)
library(kableExtra)
```

@@

# Data
\
The research uses the R language[@rstudio] as its foundation. I have used packages such as tidyverse[@tidy], here[@here], and readr[@readr] to prepare data for this project. I then used dplyr[@dplyr], KableExtra[@extra] and knitr[@knitr] to generate table ; patchwork[patch] and ggplot2[@ggplot2] to generate and organize plots.
\
```{r,warning=FALSE, message=FALSE}
#read the raw data in
raw_data <- read_csv(here("inputs/data/HS_JPvars-only_11Jan2019_complete-cases-only.csv"))
#add two columns into the data, one represents the mean positive affect for each participate over 10days,
#the other one represents the mean negative affect for each participate over 10days.
raw_data<-raw_data%>%group_by(idPartID)%>%
  mutate(mean_pos_affect=(mean(tsHiArPosAffect)+mean(tsLoArPosAffect))*1/2,
         mean_neg_affect=(mean(tsHiArNegAffect)+mean(tsLoArNegAffect))*1/2)
#rename my interested column and add them as new columns in our data
raw_data<-raw_data %>% 
  mutate(sub_health=as.numeric(idSubOverallWellbeing),,age=as.numeric(idAge),gender=as.numeric(idGender),
         network_size=as.numeric(idSocNetworkSize),social_quality=as.numeric(idSocRelQuality),
         self_efficacy=as.numeric(idSocSelfEfficacy),self_reflection=as.numeric(idSelfReflection),
         anxiety=as.numeric(idSocAnxiety),solitude=as.numeric(idOverSolitude))
#select columns 
clean_data<-raw_data%>%
  select(idPartID,tsAssessNumber,sub_health,age,gender,network_size,social_quality,self_efficacy,self_reflection,solitude,anxiety,mean_pos_affect,mean_neg_affect)
#filter out replicate rows to get each participate's data
clean_data<-clean_data%>%
  filter(tsAssessNumber==1)
#filter out NAs
clean_data<-clean_data%>%
  filter(!is.na(sub_health)&!is.na(age)&!is.na(gender)&!is.na(network_size)&!is.na(social_quality)&!is.na(self_efficacy)&!is.na(self_reflection)&!is.na(solitude)&!is.na(anxiety)&!is.na(mean_pos_affect)&!is.na(mean_pos_affect)&!is.na(idPartID)&!is.na(tsAssessNumber))
#delete the column for assesment number and get my final data
final_data<-clean_data%>%
   select(idPartID,sub_health,age,gender,network_size,social_quality,self_efficacy,self_reflection,solitude,anxiety,mean_pos_affect,mean_neg_affect)
#write the final data in a csv file and put it in the input folder
write_csv(final_data, here("inputs/data/final_data.csv"))
```

## Data Source and the Experiment
The original dataset was gathered during a 2018 experiment at the University of British Columbia. One hundred community-dwelling adults aged 50–85 years (64 percent female; 56 percent East Asian, 36 percent European, 8% other/mixed heritage) and 50 students aged 18–28 years (92 percent female; 42 percent East Asian, 22 percent European, 36 percent other/mixed heritage) each completed approximately 30 daily life assessments on their current and desired social situation, thoughts, and affect over ten days for this experiment[@hopp]. A baseline session, a time-sampling phase, and an exit session were all part of this experiment. Participants completed questionnaires evaluating individual differences (e.g., trait self-reflection) and were trained to use portable electronic devices during the baseline session. Then, starting the day after the baseline session, individuals were beeped three times daily (once in the morning, once in the afternoon, and once in the evening) over a 10-day time sampling period. On each occasion, participants used a touch screen interface on an iPod or iPad mini to answer a brief questionnaire about their thoughts, feelings, and existing and ideal social situation [@hopp].\

@@

There are 4571 rows and 51 variables in the original dataset. It contains all the experimental survey results from 150 observations; each participant completed the same survey around 30 times over ten days (3 to 4 times a day). As a result, each survey is recorded in one row. Thus each participant's response is stored in 30 rows. Individual differences (person-level) and temporal sampling (momentary level) variables are included in this dataset. Individual difference variables are collected before and after the trials; this variable contains participants' personal information such as age, gender, and social network size. Every participant's different variables in each row are the same.On the other hand, the time sampling variables contain the data gathered during the experiments. The sampling variables' results are unique in every single row. Every row has a different set of results for the sampling variables. Every participant's number of surveys (from 1 to 30) was recorded in a variable named Assessment Number[@hopp].\
I did some data cleaning on the original data set because I intend to investigate the potential correlation between the selected factors (age, gender, rate of overall well-being, social network size, social relationship quality, social self-efficacy, self-reflection, solitude time, and anxiety level) and both positive and negative solitude experiences. First, I calculate the mean value of each participant's positive affect (average of the high-arousal positive affect and low-arousal positive affect) and negative affect((average of the high-arousal negative affect and low-arousal negative affect) and save them into these two variable columns for further use. Then, I filter out all rows whose assessment number does not equal 1. This method allows me to obtain individual differences and the mean value of positive and negative solitude emotion scores over ten days, with each row representing a unique participant. Then I remove all of the empty cells. Finally, I chose all of the required variables to create the final dataset I need for this study.
The definitions of the variables in the cleaned data are shown below.\

```{r,warning=FALSE}
vardef=data_frame("Variables"=c("sub_health", "age", "gender", "network_size", "social quality", "self_efficacy", "self_reflection", "solitude", "anxiety", "mean_pos_affect", "mean_neg_affect"),
                  "Definition"=c("The rate of the overall wellbeing on the scale of 5", "Age at baseline session in years", "1 = female, 0 = male", "Total network size", "The social relationship quality of participants on the scale of 5","Social self-efficacy score on the scale of 5","Self-reflection score on the scale of 5","Overall time in solitude in proportion","Personal anxiety score for their social relationship on the scale of 5","The average positive solitude experience in 10 days","The average negative solitude experience in 10 days"))
knitr::kable(vardef,caption="Definitions of Variables")
```

@@

```{r dis,fig.cap="Distribution of solitude experiences",fig.position="H"}
#add two new columns 
Positive_solitude <- final_data%>%mutate(value=mean_pos_affect)
Negative_solitude <-final_data%>%mutate(value=mean_neg_affect)
#combine the two dataframes into one.  
Positive_solitude$Experience_type <- 'Positive solitude experience'
Negative_solitude$Experience_type <- 'Negative solitude experience'
exp <- rbind(Positive_solitude, Negative_solitude)
#draw the plot
ggplot(exp, aes(value, fill = Experience_type)) + 
   geom_histogram(alpha = 0.4, position = 'identity',bins = 23)
```

@@

```{r pos,fig.cap="Relationship between the social quality and the positive solitude experiences",fig.width=6,fig.height=2, message=FALSE}
final_data%>%
  ggplot(aes(x=social_quality,y=mean_pos_affect,)) +labs(x="social quality",y="Positive solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r neg,fig.cap="Relationship between the social quality and the positive solitude experiences",fig.width=6,fig.height=2,message=FALSE}
final_data%>%
  ggplot(aes(x=social_quality,y=mean_neg_affect,)) +labs(x="social quality",y="Negative solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")
```

From the above graphs, we can observe linear trends in both plots. Better social quality will lead to a higher score on the positive solitude affect(Figure \@ref(fig:pos)), which means a positive linear relationship between the positive solitude experience and the social quality. As for another graph, on the other hand, we can notice that as the social quality becomes better, the score on negative solitude experiences gets lower(Figure \@ref(fig:neg)), which means that there is a negative linear relationship between the negative solitude experiences and the social quality. These facts imply that better quality is helpful for people to get a better solitude experience.

```{r den, fig.cap="Relationship between the social quality and the network size"}
final_data %>% ggplot(aes(x = network_size, y = social_quality)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon", colour = "white") + labs(
    x = "network size",
    y = "social quality",
  )+
  theme(panel.background = element_rect(fill = "gray98"),
    panel.grid.major.y = element_line(
      color = "gray",
      size = 0.5,
      linetype = 1
    ),
    axis.line =  element_line(
      color = "black",
      size = 0.5,
      linetype = 1
    )
  )
```

Due to the rapid development of technology, social media has become a considerable component of people's social life. Thus, I assume primarily that the network size will influence the social quality to a great extent. However, I am not sure whether this influence will be good or bad. Because spending too much time on the social media will be beneficial for some people since social media helps them to keep in touch with their friends more quickly, but it will also harm people's social quality since people will have less time to hang out and communicate with their friends in real life. To investigate further the relationship between the social quality and the network size, I use our trimmed dataset to plot a density graph(Figure \@ref(fig:den)). From the above plot, I observed that participants with high network size(total network size greater than 30) tend to have better social quality(with a score on social media more significant than 3). As for the people with relatively smaller network sizes, we can see that their scores on social quality range from the lowest to the highest. But we can still observe that most people with relatively smaller network sizes are still getting a pretty satisfactory score on the social quality at around 3.5. According to the above observations, we can conclude that the network size may have a little bit positive effect on social quality. Still, there is no sign that it dramatically impacts social quality.\

@@

```{r ag, message=FALSE,fig.cap="Relationship between the anxiety and the solitude experiences based on gender"}
p1<-final_data%>%mutate(Gender=case_when(gender==1~"female", gender==0~"male"))%>%
  ggplot(aes(x=anxiety,y=mean_pos_affect,color=Gender)) +labs(x="anxiety",y="Positivee solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")

p2<-final_data%>%mutate(Gender=case_when(gender==1~"female", gender==0~"male"))%>%
  ggplot(aes(x=anxiety,y=mean_neg_affect,color=Gender)) +labs(x="anxiety",y="Negative solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")

p1+p2

@@

```{r box, fig.caption="Relationship between the age and the solitude experiences"}
p3<-final_data%>%
  mutate(Age_group=case_when(age<50~"Student",age>=49~"Older adult"))%>%
  ggplot(aes(y=mean_pos_affect, x=Age_group))+geom_boxplot(color="black",fill="light blue")+labs(x="Age group",y="Positive solitude affect")+ coord_flip()

p4<-final_data%>%
  mutate(Age_group=case_when(age<50~"Student",age>=49~"Older adult"))%>%
  ggplot(aes(y=mean_neg_affect, x=Age_group))+geom_boxplot(color="black",fill="light blue")+labs(x="Age group",y="Negatice solitude affect")+ coord_flip()

p3+p4

@@

In the original experiment, all participants were divided into two groups based on age. The participants are divided into one hundred community‐dwelling adults aged 50–85 years and 50 undergraduate students aged 18–28 years. I did the same grouping on age for my dataset. I plot two boxplots(Figure \@ref(fig:box)) to compare the score on positive and negative solitude experiences between different age groups. Based on my common sense, I will claim that the older group will have a better solitude experience because they are more mature than the students. They can handle the negative affect when being isolated. Now, I will look at the above graphs(Figure \@ref(fig:box)) to check whether my assumptions are correct. For the positive solitude affect(plot on the left), we notice that the older adult group has a mean score of around 60, which is much higher than the student group. As for the negative solitude affect, on the other hand, the student group has a higher score on the negative solitude affect than the older adult group. These facts match my assumption well.

@@

```{r ,echo=FALSE, include=FALSE}
pos_mod=lm(mean_pos_affect~age+gender+network_size+social_quality+self_efficacy+self_reflection+solitude+anxiety+sub_health,data=final_data)
neg_mod=lm(mean_neg_affect~age+gender+network_size+social_quality+self_efficacy+self_reflection+solitude+anxiety+sub_health,data=final_data)
summary(pos_mod)
summary(neg_mod)
pos_vif=vif(pos_mod)
neg_vif=vif(neg_mod)
```

@@

I fit two models using all of the selected variables, one for the positive solitude affect and the other one for the negative solitude affect. The variables are age, gender, the rate of overall well being, social network size, social relationship quality, social self-efficacy, the self-reflection, solitude time, and anxiety level.\
From the below table 2, we can see that all of the VIF values are relatively small. So, we decided to keep all those variables in the full models. Then, I use the backward selection to help me select the best model. Our full model for positive solitude affect contains nine variables: age, gender, the rate of overall well-being, social network size, social relationship quality, social self-efficacy, self-reflection, solitude time, and anxiety level. The backward selection model removes six variables from my full model. Thus, the backward selection model for the positive solitude experiences has only three variables; age, social quality, and self-efficacy. And those variables are concluded as having the most correlation with the positive solitude experiences. Our full model for the negative solitude affect contains nine variables as well. The backward selection model also removes six variables from my full model. Thus, the backward selection model for the negative solitude affect has three variables; age, social quality, and anxiety level. And those variables are concluded as having the most correlation with the negative solitude affect.\

```{r tab, }
Variable_pos <- c("age","gender","network_size","social_quality","self_efficacy","self_reflection","solitude",
                  "anxiety","sub_health")
Variable_neg <- c("age","gender","network_size","social_quality","self_efficacy","self_reflection","solitude",
                  "anxiety","sub_health")
vif_table<-data.frame(Variable_pos, pos_vif,Variable_neg, neg_vif)
knitr::kable(vif_table, col.names = c("variables of positive solitude model", "vif value", "variables of negative solitude model", "vif value"), caption = "VIF value for the full linear models")%>%
  kable_styling(latex_options = "HOLD_position")
```

@@

```{r ,echo=FALSE, include=FALSE}
m = length(final_data$mean_pos_affect)
bic_pos = step(pos_mod, direction = "backward", k = log(m))
n = length(final_data$mean_neg_affect)
bic_pos = step(neg_mod, direction = "backward", k = log(n))
final_pos_mod =lm(mean_pos_affect~age+social_quality+self_efficacy,data=final_data)
summary(final_pos_mod)
final_neg_mod =lm(mean_neg_affect~age+social_quality+anxiety,data=final_data)
summary(final_neg_mod)
```

@@

Now, we can finally analyze our linear regression models. Let us first look at the model for the positive solitude affect. The following table includes the estimated result for this model(table3).

```{r}
varp=c("intercept","age","social_quality","self_efficacy")
estp=c(0.74659,0.24844,5.96085,5.78392)
pp=c(0.915136,1.8*10^(-8),0.000221,0.001318)
mod1_table=data.frame("variables"=varp, "estimations"=estp,"p_values"=pp)
knitr::kable(mod1_table,caption="The estimations and the p values for the positive solitude affect model")%>%
  kable_styling(latex_options = "HOLD_position")
```

We first look at $\hat{\beta}_0$. This value is the intercept of our linear regression models. It means when the other variable equals 0. Accordingly, our score on positive solitude is 0.74659, which is almost 0. This result is meaningless in an actual situation since the score for the positive solitude can hardly be 0. Also, we found out that the p-value for the intercept is more significant than the significance level of 0.05, which further proves my statement that this intercept estimate is meaningless. Then, for all of the predictors, we can find out that all p values are less than the significance level of 0.05. Therefore, I conclude that we have strong evidence to support our null hypothesis; thus, the positive solitude affect is highly correlated with age, social quality, and self-efficacy.\
Now, let's discuss the estimations for each preditor. The estimate for the age is 0.24844, which means that one year increase in age while holding other variables constant will lead to a 0.24844 increase in the score for the positive solitude experience. This result shows that age has a positive relationship with the positive solitude affect, as we expect, but the impact on the positive solitude affect is relatively tiny. As for the social quality, the estimation for the social_quality is 5.96085, which means that one score increase in the social_qualoity while holding other variables constant will lead to a 5.96085 increase in the score for the positive solitude experience. This result shows that the social_quality do a positive relationship with the positive solitude affect, as we expect, and the impact on the positive solitude affect is significant. Lastly, for the self-efficacy, since we have not dived into this concept earlier in this paper, I will first introduce what self-efficacy refers to. Self-efficacy refers to an individual's belief in their capacity to execute behaviors necessary to produce specific performance attainments[@american]. The estimation for the social_quality is 5.78392, which means that one score increase in the self_efficacy while holding other variables constant will lead to a 5.78392 increase in the score for the positive solitude experience. This result shows that the self_efficacy has a positive relationship with the positive solitude affect and significantly impacts the positive solitude affect.

Let's also look at the model for the negative solitude affect. The following table includes the estimated results for this model(table4).

```{r}
varn=c("intercept","age","social_quality","anxiety")
estn=c(50.09895,-0.14323,-6.83339,4.33072)
pn=c(2.82*10^-7,0.00695,0.00014,0.00743)
mod2_table=data.frame("variables"=varn, "estimations"=estn,"p_values"=pn)
knitr::kable(mod2_table,caption="The estimations and the p values for the negative solitude affect model")%>%
  kable_styling(latex_options = "HOLD_position")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width=8,fig.height=4)
library(readr)
library(here)
library(tidyverse)
library(dplyr)
library(patchwork)
library(kableExtra)
library(car)
```

@@

# Data
\
The research uses the R language[@rstudio] as its foundation. I have used packages such as tidyverse[@tidy], here[@here], car[@car] and readr[@readr] to prepare data and models for this project. I then used dplyr[@dplyr], KableExtra[@extra] and knitr[@knitr] to generate table ; patchwork[@patch] and ggplot2[@ggplot2] to generate and organize plots.
\
```{r,warning=FALSE, message=FALSE}
#read the raw data in
raw_data <- read_csv(here("inputs/data/HS_JPvars-only_11Jan2019_complete-cases-only.csv"))
#add two columns into the data, one represents the mean positive affect for each participate over 10days,
#the other one represents the mean negative affect for each participate over 10days.
raw_data<-raw_data%>%group_by(idPartID)%>%
  mutate(mean_pos_affect=(mean(tsHiArPosAffect)+mean(tsLoArPosAffect))*1/2,
         mean_neg_affect=(mean(tsHiArNegAffect)+mean(tsLoArNegAffect))*1/2)
#rename my interested column and add them as new columns in our data
raw_data<-raw_data %>% 
  mutate(sub_health=as.numeric(idSubOverallWellbeing),,age=as.numeric(idAge),gender=as.numeric(idGender),
         network_size=as.numeric(idSocNetworkSize),social_quality=as.numeric(idSocRelQuality),
         self_efficacy=as.numeric(idSocSelfEfficacy),self_reflection=as.numeric(idSelfReflection),
         anxiety=as.numeric(idSocAnxiety),solitude=as.numeric(idOverSolitude))
#select columns 
clean_data<-raw_data%>%
  select(idPartID,tsAssessNumber,sub_health,age,gender,network_size,social_quality,self_efficacy,self_reflection,solitude,anxiety,mean_pos_affect,mean_neg_affect)
#filter out replicate rows to get each participate's data
clean_data<-clean_data%>%
  filter(tsAssessNumber==1)
#filter out NAs
clean_data<-clean_data%>%
  filter(!is.na(sub_health)&!is.na(age)&!is.na(gender)&!is.na(network_size)&!is.na(social_quality)&!is.na(self_efficacy)&!is.na(self_reflection)&!is.na(solitude)&!is.na(anxiety)&!is.na(mean_pos_affect)&!is.na(mean_pos_affect)&!is.na(idPartID)&!is.na(tsAssessNumber))
#delete the column for assesment number and get my final data
final_data<-clean_data%>%
   select(idPartID,sub_health,age,gender,network_size,social_quality,self_efficacy,self_reflection,solitude,anxiety,mean_pos_affect,mean_neg_affect)
#write the final data in a csv file and put it in the input folder
write_csv(final_data, here("inputs/data/final_data.csv"))
```

## Data Source and the Experiment
The original dataset was gathered during a experiment at the University of British Columbia. One hundred community-dwelling adults aged 50–85 years (64 percent female; 56 percent East Asian, 36 percent European, 8% other/mixed heritage) and 50 students aged 18–28 years (92 percent female; 42 percent East Asian, 22 percent European, 36 percent other/mixed heritage) each completed approximately 30 daily life assessments on their current and desired social situation, thoughts, and affect over ten days for this experiment[@hopp]. A baseline session, a time-sampling phase, and an exit session were all part of this experiment. Participants completed questionnaires evaluating individual differences (e.g., trait self-reflection) and were trained to use portable electronic devices during the baseline session. Then, starting the day after the baseline session, individuals were beeped three times daily (once in the morning, once in the afternoon, and once in the evening) over a 10-day time sampling period. On each occasion, participants used a touch screen interface on an iPod or iPad mini to answer a brief questionnaire about their thoughts, feelings, and existing and ideal social situation [@hopp].\

@@

There are 4571 rows and 51 variables in the original dataset. It contains all the experimental survey results from 150 observations; each participant completed the same survey around 30 times over ten days (3 to 4 times a day). As a result, each survey is recorded in one row. Thus each participant's response is stored in 30 rows. Individual differences (person-level) and temporal sampling (momentary level) variables are included in this dataset. Individual difference variables are collected before and after the trials; this variable contains participants' personal information such as age, gender, and social network size. Every participant's different variables in each row are the same.On the other hand, the time sampling variables contain the data gathered during the experiments. The sampling variables' results are unique in every single row. Every row has a different set of results for the sampling variables. Every participant's number of surveys (from 1 to 30) was recorded in a variable named Assessment Number[@hopp].\
I did some data cleaning on the original data set because I intend to investigate the potential correlation between the selected factors (age, gender, rate of overall well-being, social network size, social relationship quality, social self-efficacy, self-reflection, solitude time, and anxiety level) and both positive and negative solitude experiences. First, I calculate the mean value of each participant's positive affect (average of the high-arousal positive affect and low-arousal positive affect) and negative affect((average of the high-arousal negative affect and low-arousal negative affect) and save them into these two variable columns for further use. Then, I filter out all rows whose assessment number does not equal 1. This method allows me to obtain individual differences and the mean value of positive and negative solitude emotion scores over ten days, with each row representing a unique participant. Then I remove all of the empty cells. Finally, I chose all of the required variables to create the final dataset I need for this study.
The definitions of the variables in the cleaned data are shown in the above table(Table \@ref(tab:tab1)).\

```{r tab1,warning=FALSE}
#create data frame 
vardef=data_frame("Variables"=c("sub_health", "age", "gender", "network_size", "social quality", "self_efficacy", "self_reflection", "solitude", "anxiety", "mean_pos_affect", "mean_neg_affect"),
                  "Definition"=c("The rate of the overall wellbeing on the scale of 5", "Age at baseline session in years", "1 = female, 0 = male", "Total network size", "The social relationship quality of participants on the scale of 5","Social self-efficacy score on the scale of 5","Self-reflection score on the scale of 5","Overall time in solitude in proportion","Personal anxiety score for their social relationship on the scale of 5","The average positive solitude experience in 10 days","The average negative solitude experience in 10 days"))
#generate table and add caption
knitr::kable(vardef,caption="Definitions of Variables")
```

@@

```{r dis,fig.cap="Distribution of solitude experiences"}
#add two new columns 
Positive_solitude <- final_data%>%mutate(value=mean_pos_affect)
Negative_solitude <-final_data%>%mutate(value=mean_neg_affect)
#combine the two dataframes into one.  
Positive_solitude$Experience_type <- 'Positive solitude experience'
Negative_solitude$Experience_type <- 'Negative solitude experience'
exp <- rbind(Positive_solitude, Negative_solitude)
#draw the plot
ggplot(exp, aes(value, fill = Experience_type)) + 
   geom_histogram(alpha = 0.4, position = 'identity',bins = 23)
```

@@

```{r pos,fig.cap="Relationship between the social quality and the positive solitude experiences",fig.width=6,fig.height=2, message=FALSE}
#draw the scatterplot for pos
final_data%>%
  ggplot(aes(x=social_quality,y=mean_pos_affect,)) +labs(x="social quality",y="Positive solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r neg,fig.cap="Relationship between the social quality and the positive solitude experiences",fig.width=6,fig.height=2,message=FALSE}
#draw the scatterplot fot neg
final_data%>%
  ggplot(aes(x=social_quality,y=mean_neg_affect,)) +labs(x="social quality",y="Negative solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")
```

From the above graphs(Figure \@ref(fig:pos))(Figure \@ref(fig:neg)), we can observe linear trends in both plots. Better social quality will lead to a higher score on the positive solitude affect(Figure \@ref(fig:pos)), which means a positive linear relationship between the positive solitude experience and the social quality. As for another graph, on the other hand, we can notice that as the social quality becomes better, the score on negative solitude experiences gets lower(Figure \@ref(fig:neg)), which means that there is a negative linear relationship between the negative solitude experiences and the social quality. These facts imply that better quality is helpful for people to get a better solitude experience.

```{r den, fig.cap="Relationship between the social quality and the network size"}
#draw the density plot
final_data %>% ggplot(aes(x = network_size, y = social_quality)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon", colour = "white") + labs(
    x = "network size",
    y = "social quality",
  )+
  theme(panel.background = element_rect(fill = "gray98"),
    panel.grid.major.y = element_line(
      color = "gray",
      size = 0.5,
      linetype = 1
    ),
    axis.line =  element_line(
      color = "black",
      size = 0.5,
      linetype = 1
    )
  )
```

Due to the rapid development of technology, social media has become a considerable component of people's social life. Thus, I assume primarily that the network size will influence the social quality to a great extent. However, I am not sure whether this influence will be good or bad. Because spending too much time on the social media will be beneficial for some people since social media helps them to keep in touch with their friends more quickly, but it will also harm people's social quality since people will have less time to hang out and communicate with their friends in real life. To investigate further the relationship between the social quality and the network size, I use our trimmed dataset to plot a density graph(Figure \@ref(fig:den)). From the above plot(Figure \@ref(fig:den)), I observed that participants with high network size(total network size greater than 30) tend to have better social quality(with a score on social media more significant than 3). As for the people with relatively smaller network sizes, we can see that their scores on social quality range from the lowest to the highest. But we can still observe that most people with relatively smaller network sizes are still getting a pretty satisfactory score on the social quality at around 3.5. According to the above observations, we can conclude that the network size may have a little bit positive effect on social quality. Still, there is no sign that it dramatically impacts social quality.\

@@

```{r ag, message=FALSE,fig.cap="Relationship between the anxiety and the solitude experiences based on gender"}
#add a new column Gender and draw the scatterplot for pos
p1<-final_data%>%mutate(Gender=case_when(gender==1~"female", gender==0~"male"))%>%
  ggplot(aes(x=anxiety,y=mean_pos_affect,color=Gender)) +labs(x="anxiety",y="Positivee solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")
#add a new column Gender and draw the scatterplot for neg
p2<-final_data%>%mutate(Gender=case_when(gender==1~"female", gender==0~"male"))%>%
  ggplot(aes(x=anxiety,y=mean_neg_affect,color=Gender)) +labs(x="anxiety",y="Negative solitude experiences")+
  geom_point()+
  geom_smooth(method = "lm")
#rearrange the plots
p1+p2

@@

```{r boxp,fig.cap="Relationship between the age group and the solitude experiences"}
#add a new column age group and draw the boxplot for pos
p3<-final_data%>%
  mutate(Age_group=case_when(age<50~"Student",age>=49~"Older adult"))%>%
  ggplot(aes(y=mean_pos_affect, x=Age_group))+geom_boxplot(color="black",fill="light blue")+labs(x="Age group",y="Positive solitude affect")+ coord_flip()
#add a new column age group and draw the boxplot for neg
p4<-final_data%>%
  mutate(Age_group=case_when(age<50~"Student",age>=49~"Older adult"))%>%
  ggplot(aes(y=mean_neg_affect, x=Age_group))+geom_boxplot(color="black",fill="light blue")+labs(x="Age group",y="Negatice solitude affect")+ coord_flip()
#rearrange the plots
p3+p4

@@

\
In the original experiment, all participants were divided into two groups based on age. The participants are divided into one hundred community‐dwelling adults aged 50–85 years and 50 undergraduate students aged 18–28 years. I did the same grouping on age for my dataset. I plot two boxplots(Figure \@ref(fig:boxp)) to compare the score on positive and negative solitude experiences between different age groups. Based on my common sense, I will claim that the older group will have a better solitude experience because they are more mature than the students. They can handle the negative affect when being isolated. Now, I will look at the above graphs(Figure \@ref(fig:boxp)) to check whether my assumptions are correct. For the positive solitude affect(plot on the left), we notice that the older adult group has a mean score of around 60, which is much higher than the student group. As for the negative solitude affect, on the other hand, the student group has a higher score on the negative solitude affect than the older adult group. These facts match my assumption well.

@@

```{r ,echo=FALSE, include=FALSE}
#fit model for pos
pos_mod=lm(mean_pos_affect~age+gender+network_size+social_quality+self_efficacy+self_reflection+solitude+anxiety+sub_health,data=final_data)
#fit model for neg
neg_mod=lm(mean_neg_affect~age+gender+network_size+social_quality+self_efficacy+self_reflection+solitude+anxiety+sub_health,data=final_data)
summary(pos_mod)
summary(neg_mod)
#check vif for pos_mod
pos_vif=vif(pos_mod)
#check vif for neg_mod
neg_vif=vif(neg_mod)
```

@@

I fit two models using all of the selected variables, one for the positive solitude affect and the other one for the negative solitude affect. The variables are age, gender, the rate of overall well being, social network size, social relationship quality, social self-efficacy, the self-reflection, solitude time, and anxiety level.\
From the below table(Table \@ref(tab:vif), we can see that all of the VIF values are relatively small. So, we decided to keep all those variables in the full models. Then, I use the backward selection to help me select the best model. Our full model for positive solitude affect contains nine variables: age, gender, the rate of overall well-being, social network size, social relationship quality, social self-efficacy, self-reflection, solitude time, and anxiety level. The backward selection model removes six variables from my full model. Thus, the backward selection model for the positive solitude experiences has only three variables; age, social quality, and self-efficacy. And those variables are concluded as having the most correlation with the positive solitude experiences. Our full model for the negative solitude affect contains nine variables as well. The backward selection model also removes six variables from my full model. Thus, the backward selection model for the negative solitude affect has three variables; age, social quality, and anxiety level. And those variables are concluded as having the most correlation with the negative solitude affect.\

```{r vif}
#create dataframe and generate table
Variable_pos <- c("age","gender","network_size","social_quality","self_efficacy","self_reflection","solitude",
                  "anxiety","sub_health")
Variable_neg <- c("age","gender","network_size","social_quality","self_efficacy","self_reflection","solitude",
                  "anxiety","sub_health")
vif_table<-data.frame(Variable_pos, pos_vif,Variable_neg, neg_vif)
knitr::kable(vif_table, col.names = c("variables of positive solitude model", "vif value", "variables of negative solitude model", "vif value"), caption = "VIF value for the full linear models")%>%
  kable_styling(latex_options = "HOLD_position")
```

@@

```{r ,echo=FALSE, include=FALSE}
m = length(final_data$mean_pos_affect)
#bic backward selection for pos_mod
bic_pos = step(pos_mod, direction = "backward", k = log(m))
n = length(final_data$mean_neg_affect)
#bic backward seclection for neg_mod
bic_neg = step(neg_mod, direction = "backward", k = log(n))
#fit final model for pos
final_pos_mod =lm(mean_pos_affect~age+social_quality+self_efficacy,data=final_data)
summary(final_pos_mod)
#fit final model for neg
final_neg_mod =lm(mean_neg_affect~age+social_quality+anxiety,data=final_data)
summary(final_neg_mod)
```

@@

Now, we can finally analyze our linear regression models. Let us first look at the model for the positive solitude affect. The following table includes the estimated result for this model(Table \@ref(tab:post)).

```{r post}
#create dataframe and generate table
varp=c("intercept","age","social_quality","self_efficacy")
estp=c(0.74659,0.24844,5.96085,5.78392)
pp=c(0.915136,1.8*10^(-8),0.000221,0.001318)
mod1_table=data.frame("variables"=varp, "estimations"=estp,"p_values"=pp)
knitr::kable(mod1_table,caption="The estimations and the p values for the positive solitude affect model")%>%
  kable_styling(latex_options = "HOLD_position")
```

We first look at $\hat{\beta}_0$. This value is the intercept of our linear regression models. It means when the other variable equals 0. Accordingly, our score on positive solitude is 0.74659, which is almost 0. This result is meaningless in an actual situation since the score for the positive solitude can hardly be 0. Also, we found out that the p-value for the intercept is more significant than the significance level of 0.05, which further proves my statement that this intercept estimate is meaningless. Then, for all of the predictors, we can find out that all p values are less than the significance level of 0.05. Therefore, I conclude that we have strong evidence to support our null hypothesis; thus, the positive solitude affect is highly correlated with age, social quality, and self-efficacy.\
Now, let's discuss the estimations for each predictor. The estimate for the age is 0.24844, which means that one year increase in age while holding other variables constant will lead to a 0.24844 increase in the score for the positive solitude experience. This result shows that age has a positive relationship with the positive solitude affect, as we expect, but the impact on the positive solitude affect is relatively tiny. As for the social quality, the estimation for the social_quality is 5.96085, which means that one score increase in the social_qualoity while holding other variables constant will lead to a 5.96085 increase in the score for the positive solitude experience. This result shows that the social_quality do a positive relationship with the positive solitude affect, as we expect, and the impact on the positive solitude affect is significant. Lastly, for the self-efficacy, since we have not dived into this concept earlier in this paper, I will first introduce what self-efficacy refers to. Self-efficacy refers to an individual's belief in their capacity to execute behaviors necessary to produce specific performance attainments[@american]. The estimation for the social_quality is 5.78392, which means that one score increase in the self_efficacy while holding other variables constant will lead to a 5.78392 increase in the score for the positive solitude experience. This result shows that the self_efficacy has a positive relationship with the positive solitude affect and significantly impacts the positive solitude affect.

Let's also look at the model for the negative solitude affect. The following table includes the estimated results for this model(Table \@ref(tab:negt).

```{r negt}
#create dataframe and generate table
varn=c("intercept","age","social_quality","anxiety")
estn=c(50.09895,-0.14323,-6.83339,4.33072)
pn=c(2.82*10^-7,0.00695,0.00014,0.00743)
mod2_table=data.frame("variables"=varn, "estimations"=estn,"p_values"=pn)
knitr::kable(mod2_table,caption="The estimations and the p values for the negative solitude affect model")%>%
  kable_styling(latex_options = "HOLD_position")
```

@@

## Data Sheet

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The original dataset was gathered during a experiment at the University of British Columbia. One hundred community-dwelling adults aged 50–85 years (64 percent female; 56 percent East Asian, 36 percent European, 8% other/mixed heritage) and 50 students aged 18–28 years (92 percent female; 42 percent East Asian, 22 percent European, 36 percent other/mixed heritage) each completed approximately 30 daily life assessments on their current and desired social situation, thoughts, and affect over ten days for this experiment. It was used to investigate the predictors of distinct types of solitude experiences in daily life.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Jennifer C. Lay, Theresa Pauly, Peter Graf, Jeremy C. Biesanz and Christiane A. Hoppmann from department of Psychology inUniversity of British Columbia created this dataset.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Vancouver Foundation grant to Christiane Hoppmann, Sandra Petrozzi, Atiya Mahmood, and Peter Graf; University of British Columbia Faculty of Arts grant to Christiane Hoppmann; University of British Columbia Alpha Mater Society grant to Jennifer Lay; support from Michael Smith Foundation for Health Research and
the Canada Research Chairs Programme to Christiane Hoppmann; support from Social Sciences and Humanities Research Council of Canada (Vanier CGS Program) to Jennifer Lay.
4. *Any other comments?*
    - No
